A thesis draft

### 2018-10-04 draft.tex
Add description about ETSI software architecture

In the original VIBES architectural design, based on leveraging virtualization 
technologies, is possible to identify different macro-components, each of these 
specialized in fullfilling a specific goal. For the ETSI standards, the Network 
Function Virtualization (NFV) design should be composed as follows:\todo{Insert 
image page 11 ETSI vibes specification}
\begin{itemize}
 \item Network Function Virtualization Infrastructure (NFVI): it's the heart of 
the whole computation component, and here three sub-domains can be identified:
\todo{Expand this section}
\begin{itemize} 
 \item Hypervisor domain that is composed of the Virtual Compute, the Virtual 
Storage, and the Virtualization Layer. These components
 \item Compute domain composed by the Physical Compute and the Physical Storage
 \item Infrastructure domain which has the Physical Network, and its 
virtualized counterpart as made available by the Virtualization Layer
\end{itemize}

>>>>

In the original VIBES architectural design, based on leveraging virtualization 
technologies, is possible to identify different macro-components, each of these 
specialized in fullfilling a specific goal. For the ETSI standards, the Network 
Function Virtualization (NFV) design should be composed as follows:\todo{Insert 
image page 11 ETSI vibes specification}
\begin{itemize}
 \item Network Function Virtualization Infrastructure (NFVI): it's the heart of 
the whole computation component, and here three sub-domains can be identified:
\todo{Expand this section}
\begin{itemize} 
 \item \textbf{Hypervisor domain} that is composed of the Virtual Compute, the 
Virtual Storage, and the Virtualization Layer. These components are used to 
virtualize the computational and storage resources, providing a layer for 
accessing it.
 \item \textbf{Compute domain} composed by the Physical Compute and the 
Physical Storage. These are the real resources which are virtualized via 
software.
 \item \textbf{Infrastructure domain} which has the Physical Network, and its 
virtualized counterpart as made available by the Virtualization Layer.
\end{itemize}

In conventional virtualization systems these resources are usually separated 
from the host operating system, providing better isolation but worste 
performance. The ETSI infrastructure, instead, tries with container 
virtualization technology to push for a better NFV responsiveness\todo{Check 
term - I don't think it actually exists}, removing the additional operating 
system (called ``guest'' OS) required by the usual hypervisor-oriented approach.
